DATA 621 - Business Analytics and Data Mining

### 2020-10-27 HW3/HW3_Final_AA.Rmd
more updates to help clean up work

@@

Tuning the models for best parameters.

@@

Computing the metrics for the logit model:

@@

crime_pred %>%
  conf_mat(truth = target, estimate = .pred_class)
```

@@

```{r}
logit_wf %>%
  last_fit(data_split) %>%
  collect_metrics()

>>>>

We will resample the data to tune parameters for the logistic classifier. This uses all variable as individual predictors.

@@

@@

@@

@@

```{r}
final_model_pred %>%
  conf_mat(truth = target, estimate = .pred_class)

metrics_df
